Mines Accident Prediction

### 2017-03-04 A New Hope/Catherine_Analysis.Rmd
Update Catherine_Analysis.Rmd

all_accident_violation_cleaned <- data.frame()
counter <- 1
for (x in unique(all_accident_rollover$mine_id)){
  print(counter)
  counter = counter +1
  temp <- all_accident_violation_rollover %>% filter(mine_id==x)
  i <- 1
  while( sum(temp[i,4:11],na.rm = TRUE) == 0){
    i = i+1
  }
  if(i != 1){
    temp <- temp[-c(1:15),]
  }

  i <- nrow(temp)
  while( sum(temp[i,4:11]) == 0){
    i = i-1
  }
  if(i != nrow(temp)){
    temp <- temp[-c(nrow(temp)-i:nrow(temp)),]
  }
  all_accident_violation_cleaned <- rbind(all_accident_violation_cleaned,temp)
}
all_accident_violation_cleaned
```

>>>>

all_accident_violation_cleaned <- data.frame()
counter <- 1
for (x in unique(all_accident_rollover$mine_id)[599:11830]){
  print(counter)
  counter = counter +1

  temp <- all_accident_violation_rollover %>% filter(mine_id==x)
  for ( i in 4:11){
    temp[,i] = as.numeric(temp[,i])
  }

  if(sum(temp[,4:11]) == 0) next

  #beginning
  i <- 1
  while( sum(temp[i,4:11],na.rm = TRUE) == 0){
    i = i+1
  }
  if(i != 1){
    temp <- temp[-c(1:i),]
  }

  #ending
  i <- nrow(temp)
  while( sum(temp[i,4:11]) == 0){
    i = i-1
  }
  if(i != nrow(temp)){
    temp <- temp[-c(nrow(temp)-i:nrow(temp)),]
  }

  all_accident_violation_cleaned <- rbind(all_accident_violation_cleaned,temp)

}

all_accident_violation_cleaned
temp
